Untitled

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/Procrustes_output.Rmd
reoganization

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

Correlation <- c(selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6])
Correlation<- as.numeric(Correlation)
Sum_squares <- c(selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3])
Sum_squares<- as.numeric(Sum_squares)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

Correlation <- c(selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
Correlation<- as.numeric(Correlation)
Sum_squares <- c(selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
Sum_squares<- as.numeric(Sum_squares)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
setwd("~/R_projects/Hp_pollen_experiment")

load("Data/RData/Table_s4.RData")

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
setwd("~/R_projects/Hp_pollen_experiment")

load("Data/RData/Table_s4.RData")

Correlation <- c(selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6])

Correlation<- as.numeric(Correlation)
Sum_squares <- c(selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3])
Sum_squares<- as.numeric(Sum_squares)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
setwd("~/R_projects/Hp_pollen_experiment")

load("Data/RData/Table_s4.RData")

Correlation <- c(selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])

Correlation<- as.numeric(Correlation)

Sum_squares <- c(selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
Sum_squares<- as.numeric(Sum_squares)

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/Unused_supp/Protest_plot.Rmd
reoganization

p1<-ggplot(pro_dat,aes(x=traits,y=pro_cor))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat,aes(x=traits,y=sum_squ))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat,aes(x=traits,y=signif))+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

@@

p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+labs(title="Solanaceae",x="Traits", y = "Correlation")+geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+labs(title="",x="", y = "Sum of squares")+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+labs(title="",x="", y = "Sum of squares")+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

>>>>

p1<-ggplot(pro_dat,aes(x=traits,y=pro_cor))+labs(title="All species",x="", y = "Correlation")+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat,aes(x=traits,y=sum_squ))+labs(title="",x="", y = "Sum of squares")+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat,aes(x=traits,y=signif))+labs(title="",x="Traits", y = "Significance")+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

@@

p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+labs(title="Solanaceae",x="Traits", y = "Correlation")+geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+labs(title="",x="", y = "Sum of squares")+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+labs(title="",x="Traits", y = "Significance")+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/pollen_ratios_plots.Rmd
reoganization

```
\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
ratio_sol <-readRDS("Rmd/Data/ratio_sol.RData")
barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C. annuum-I. purpurea", "S. melongena-I. aquatica", "P. integrifolia-I. aquatica", "S. lycopersicum-I aquatica","S. melongena-E. sativa", "P. integrifolia-E. sativa", "C. annuum-S. alba", "S. lycopersicum-B. rapa"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Rmd/Data/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")

>>>>

```
\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(2,13,2,4),xpd=F)
par(mfrow=c(3,1))
ratio_bra <-readRDS("Rmd/Data/ratio_bra.RData")
barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea", "B. oleracea-I. purpurea","B. rapa-I. purpurea", "S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
abline(v=50,col="black")
legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(8.3,6.8,"A) Brassicaceae")
ratio_con <-readRDS("Rmd/Data/ratio_con.RData")
barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I. purpurea-S. melongena","I. aquatica-C. annuum","I. purpurea-E. sativa","I. aquatica-S. alba"))
abline(v=50,col="black")
legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
text(9,3.5,"B) Convolvulaceae")
